A formal approach but practical approach in train regulation

### 2025-06-25 paper/main.tex
Remove old todo now addressed

Conversely, if the train program is empty (i.e. upon termination), the train stops using rule \ruleRef{Stop}.
\begin{mathpar}
	\inferrule*[left=\ruleDef{Stop}]{
		\dirFmt{d} \neq \dirStop
	}{
	\hspace{4mm}  \redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}} \\
	\reduces
	\redTuple{\guardT}{\push{\bufTrain}{\tid{id}}}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{\dirStop}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
\todo{Est ce qu'on met un évenement pour les départs/arrivée? }

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{UntilNext}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
Notice that, in \ruleRef{UntilNext}, no message is added to the buffer. since successive \su{d}{N} orders alternate directions, the next order for that train is either \ruleRef{Start} or \ruleRef{Stop}, which send the appropriate event. We prefer sending event in \ruleRef{Start} so that there is an initial event before the train initial departure.

>>>>

Conversely, if the train program is empty (i.e. upon termination), the train stops using rule \ruleRef{Stop}.
\begin{mathpar}
	\inferrule*[left=\ruleDef{Stop}]{
		\dirFmt{d} \neq \dirStop
	}{
	\hspace{4mm}  \redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}} \\
	\reduces
	\redTuple{\guardT}{\push{\bufTrain}{\tid{id}}}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{\dirStop}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{UntilNext}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
Notice that, in \ruleRef{UntilNext}, no message is added to the buffer. Since successive \su{d}{N} orders alternate directions, the next order for that train is either \ruleRef{Start} or \ruleRef{Stop}, which send the appropriate event. We prefer sending event in \ruleRef{Start} so that there is an initial event before the train initial departure.
